\begin{center}
    \section*{\fontsize{20}{20}\selectfont Chapter 2}
\end{center}



\vspace{10mm}
\section{Project Review}
\subsection{Project Overview}

The Typing Speed Tester is like a game that helps Us get better at typing on the computer. It looks nice with different colors and easy to use. We can do speed tests to see how fast We can type and even check our past scores. Storing scores in a file is cool because we can see how much we've improved over time.Overall, it's a positive tool for improving typing skills in a fun and interactive way. 


\subsection{Project Analysis}
The Typing Speed Tester is a console-based C++ program designed to assess a user's typing speed, accuracy, and provide a score based on their performance. The project incorporates various features and functionalities to create an interactive and engaging experience for users interested in evaluating their typing skills.
\vspace{5mm}

\begin{Large}
\textbf{Key Features:}
\end{Large}%

\vspace{5mm}

\textbf{ 1. User Interaction:}

\begin{itemize}
    \item The program starts with a welcome message and prompts the user to enter their name.
    \item The main menu provides options for different functionalities, including speed testing, viewing user records, accessing help, and exiting the program.
\end{itemize}

\textbf{ 2. Speed Test:}
\begin{itemize}
    \item The speed test presents the user with random sentences to type.
    \item After completing the typing task, the program evaluates the user's performance, calculating words per minute (WPM), accuracy percentage, and assigning a score.
\end{itemize}

\newpage

\textbf{ 3. User Records:}
\begin{itemize}
     \item Users can view their past performance records, including their name, letter per minute (LPM), and score.
    \item The records are stored in a file ("score.txt") for future reference.
\end{itemize}

\textbf{ 4. Help Section:}
\begin{itemize}
    \item The help section provides information about the project, its purpose, and contact details for the development team.
    \item Users can access this section for additional guidance on using the Typing Speed Tester.
\end{itemize}

\textbf{ 5. Colorful Interface:}

\begin{itemize}
    \item The program utilizes colored text to enhance the visual appeal and create a more engaging user interface.
    \item Different colors are used for headings, messages, and menu options.
\end{itemize}

\textbf{ 6. Extras Section:}
\begin{itemize}
    \item The extras section displays a banner with the project name and acknowledges the development team's rights.
\end{itemize}

\textbf{7. Delay and Clear Screen Functions:} 
\begin{itemize}
    \item The program includes functions for introducing delays and clearing the console screen, contributing to a smoother user experience.
\end{itemize}

\vspace{4mm}

% \begin{Large}
% \textbf{How to Use:}
% \end{Large}%

% \begin{itemize}
%     \item Launch the program and enter your name.
%     \item Navigate the main menu to select a desired option (speed test, user records, help, or exit). 
%     \item Follow the instructions to complete the typing speed test.
%     \item View your performance metrics and score.
%     \item Access user records or the help section for additional information.
% \end{itemize}

\vspace{5mm}



\subsection{Summary}
In Chapter 2, we delve into the exciting world of the Typing Speed Tester project. Picture this: a virtual playground for honing your typing prowers in the realm of computers. The program isn't just a run-of-the-mill typing tool. It's a vibrant game with colours that pop and a user-friendly interface that makes typing practice a joy. The Typing Speed Tester isn't just about functionality. it's a visual feast.Now, imagine future possibilities! A graphical interface could make it even more visually appealing. How about challenging friends in real-time typing battles or customizing tests to suit our fancy? The future might bring data analysis tools, offering insights into our typing trends.
